---
title: "Schema boards 2: Learning Rate"
output:
  html_document:
    number_sections: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

# Setup: load data, define variables, etc

```{r load-data-define-variables}

rm(list=ls())

source('./scripts/utils/load_all_libraries.R')

qc_filter <- T

no_first_rep_filter <- T

plot_normality     <- T
plot_fits_near_far <- F

source('./scripts/utils/load_transform_data.R')

qc_table <- import('./results/qc_check_sheets/qc_table.csv')

if (qc_filter){
        
        qc_pass_ptp <- qc_table %>%
                filter(!qc_fail_overall) %>%
                select(ptp) %>% .[[1]]
        
        
        data_summary <- data_summary %>%
                filter(ptp %in% qc_pass_ptp)
        long_data <- long_data %>%
                filter(ptp %in% qc_pass_ptp) 
        mean_by_rep_long_all_types <- mean_by_rep_long_all_types %>%
                filter(ptp %in% qc_pass_ptp)
        
}

if (no_first_rep_filter){
        
        ptp_without_first_rep <- data_summary %>%
                group_by(ptp) %>%
                summarise(no_data_first_rep = any(no_data_first_rep)) %>%
                filter(no_data_first_rep) %>% 
                ungroup() %>%
                droplevels() %>%
                select(ptp) %>% .[[1]]
        
        data_summary <- data_summary %>%
                filter(!ptp %in% ptp_without_first_rep)
        long_data <- long_data %>%
                filter(!ptp %in% ptp_without_first_rep) 
        mean_by_rep_long_all_types <- mean_by_rep_long_all_types %>%
                filter(!ptp %in% ptp_without_first_rep)        
        
}

## BF test against 0 
reportBF = function(x, digits = 4){
        round(as.numeric(as.vector(x)), digits)
}

```

# Normality checks

## Learning rate 2-parameters

```{r 2-param-learning-rates-normality-checks}

if (plot_normality){

# QQ Plot
f1 <- data_summary %>%
        ggqqplot(x = 'learning_rate_two_param') +
        ggtitle('Learning rate 2 param, RAW: QQ Plots') +
        facet_wrap(~hidden_pa_img_type) 
        
# Density plot
f2 <- data_summary %>%
        ggplot(aes(x=learning_rate_two_param,
                   y = ..density..)) +
        geom_histogram() +
        geom_density(lwd = 1,
                     color = 'red') +
        facet_wrap(~hidden_pa_img_type) +
        ggtitle('Learning rate 2 param, RAW: Histogram and Density')

print(f1)
print(f2)

}


```

```{r 2-param-learning-rates-gauss-normality-checks}

if (plot_normality){
        
# QQ Plot
f1 <- data_summary %>%
        ggqqplot(x = 'learning_rate_two_param_G') +
        ggtitle('Learning rate 2 param, gaussianized: QQ Plots') +
        facet_wrap(~hidden_pa_img_type) 
        
# Density plot
f2 <- data_summary %>%
        ggplot(aes(x=learning_rate_two_param_G,
                   y = ..density..)) +
        geom_histogram() +
        geom_density(lwd = 1,
                     color = 'red') +
        facet_wrap(~hidden_pa_img_type) +
        ggtitle('Learning rate 2 param gaussianized, RAW: Histogram and Density')

print(f1)
print(f2)

}


```


```{r 2-param-learning-rates-no-outlier-normality-checks}

if (plot_normality){
 
# QQ Plot
f1 <- data_summary %>%
        ggqqplot(x = 'learning_rate_two_param_no_outlier') +
        ggtitle('Learning rate 2 param, RAW: QQ Plots') +
        facet_wrap(~hidden_pa_img_type) 
        
# Density plot
f2 <- data_summary %>%
        ggplot(aes(x=learning_rate_two_param_no_outlier,
                   y = ..density..)) +
        geom_histogram() +
        geom_density(lwd = 1,
                     color = 'red') +
        facet_wrap(~hidden_pa_img_type) +
        ggtitle('LR 2 param no outlier: Histogram and Density')

print(f1)
print(f2)

}


```

```{r 2-param-learning-rates-no-outlier-gaussianized-normality-checks}

if (plot_normality){

# QQ Plot
f1 <- data_summary %>%
        ggqqplot(x = 'learning_rate_two_param_no_outlier_G') +
        ggtitle('Learning rate 2 param, RAW: QQ Plots') +
        facet_wrap(~hidden_pa_img_type) 
        
# Density plot
f2 <- data_summary %>%
        ggplot(aes(x=learning_rate_two_param_no_outlier_G,
                   y = ..density..)) +
        geom_histogram() +
        geom_density(lwd = 1,
                     color = 'red') +
        facet_wrap(~hidden_pa_img_type) +
        ggtitle('LR2 param, no outlier: Histogram and Density')

print(f1)
print(f2)

}


```

# Parameter plots

## 2 Param model

### Overall, across conditions

```{r learning-rates-conditions, fig.width=7}

data_summary %>%
        filter(hidden_pa_img_type == 'near_far_combined') %>%
        droplevels() %>%
        ggplot(aes(x=condition,
                   y=learning_rate_two_param_no_outlier,
                   fill=condition)) +
        geom_violin(alpha = 0.2) +
        geom_boxplot(width=0.1,
                     fatten=4,
                     outlier.shape = '') +
        geom_point(alpha = 0.2) +
        # geom_jitter(height = 0,
        #             width = 0.06,
        #             alpha = 0.3) +
        geom_line(aes(group=ptp),
                  alpha = 0.1) +
        stat_summary(fun=mean,
                     color='red',
                     size=1) +
        ggtitle('LR 2 no outlier, comparing conditions') +
        ylab('LR 2') + 
        xlab('') +
        theme(legend.position = '')

data_summary %>%
        filter(hidden_pa_img_type == 'near_far_combined') %>%
        droplevels() %>%
        ggplot(aes(x=condition,
                   y=learning_rate_two_param_no_outlier_G,
                   fill=condition)) +
        geom_violin(alpha = 0.2) +
        geom_boxplot(width=0.1,
                     fatten=4,
                     outlier.shape = '') +
        geom_point(alpha = 0.2) +
        # geom_jitter(height = 0,
        #             width = 0.06,
        #             alpha = 0.3) +
        geom_line(aes(group=ptp),
                  alpha = 0.1) +
        stat_summary(fun=mean,
                     color='red',
                     size=1) +
        ggtitle('LR 2 no outlier gaussianized, comparing conditions') +
        ylab('LR 2') + 
        xlab('') +
        theme(legend.position = '')

data_summary %>%
        filter(hidden_pa_img_type == 'near_far_combined') %>%
        droplevels() %>%
        ggplot(aes(x=condition,
                   y=learning_rate_two_param,
                   fill=condition)) +
        geom_violin(alpha = 0.2) +
        geom_boxplot(width=0.1,
                     fatten=4,
                     outlier.shape = '') +
        geom_point(alpha = 0.2) +
        # geom_jitter(height = 0,
        #             width = 0.06,
        #             alpha = 0.3) +
        geom_line(aes(group=ptp),
                  alpha = 0.1) +
        stat_summary(fun=mean,
                     color='red',
                     size=1) +
        ggtitle('LR 2 RAW, comparing conditions') +
        ylab('LR 2 RAW') + 
        xlab('') +
        theme(legend.position = '')


data_summary %>%
        filter(hidden_pa_img_type == 'near_far_combined') %>%
        droplevels() %>%
        ggplot(aes(x=condition,
                   y=learning_rate_two_param_G,
                   fill=condition)) +
        geom_violin(alpha = 0.2) +
        geom_boxplot(width=0.1,
                     fatten=4,
                     outlier.shape = '') +
        geom_point(alpha = 0.2) +
        # geom_jitter(height = 0,
        #             width = 0.06,
        #             alpha = 0.3) +
        geom_line(aes(group=ptp),
                  alpha = 0.1) +
        stat_summary(fun=mean,
                     color='red',
                     size=1) +
        ggtitle('LR 2 RAW gaussianized, comparing conditions') +
        ylab('LR 2 RAW gaussianized') + 
        xlab('') +
        theme(legend.position = '')

```


### Far vs Near:

```{r learning-rate-2-param-conditions-near-far, fig.width=7}

data_summary %>%
        filter(hidden_pa_img_type != 'all_pa') %>%
        droplevels() %>%
        
        pivot_wider(id_cols = c(ptp,
                                counterbalancing,
                                condition),
                    names_from = hidden_pa_img_type,
                    values_from = learning_rate_two_param_no_outlier) %>% 
        mutate(far_minus_near = far - near) %>%
        
        ggplot(aes(x=condition,
                   y=far_minus_near,
                   fill=condition)) +
        geom_violin(alpha = 0.2) +
        geom_boxplot(width=0.1,
                     fatten=4,
                     outlier.shape = '') +
        # geom_jitter(height = 0,
        #             width = 0.06,
        #             alpha = 0.3) +
        geom_line(aes(group=ptp),
                  alpha = 0.1) +
        geom_point(alpha = 0.2) +
        stat_summary(fun=mean,
                     color='red',
                     size=1) +
        ggtitle('LR 2 no outlier, comparing conditions, Far-Near') +
        geom_hline(yintercept = 0, linetype = 'dashed') +
        theme(legend.position = '') +
        ylab('Far minus Near') +
        xlab('')

data_summary %>%
        filter(hidden_pa_img_type != 'all_pa') %>%
        droplevels() %>%
        
        pivot_wider(id_cols = c(ptp,
                                counterbalancing,
                                condition),
                    names_from = hidden_pa_img_type,
                    values_from = learning_rate_two_param_no_outlier_G) %>% 
        mutate(far_minus_near = far - near) %>%
        
        ggplot(aes(x=condition,
                   y=far_minus_near,
                   fill=condition)) +
        geom_violin(alpha = 0.2) +
        geom_boxplot(width=0.1,
                     fatten=4,
                     outlier.shape = '') +
        # geom_jitter(height = 0,
        #             width = 0.06,
        #             alpha = 0.3) +
        geom_line(aes(group=ptp),
                  alpha = 0.1) +
        geom_point(alpha = 0.2) +
        stat_summary(fun=mean,
                     color='red',
                     size=1) +
        ggtitle('LR 2 no outlier gaussianized, comparing conditions, Far-Near') +
        geom_hline(yintercept = 0, linetype = 'dashed') +
        theme(legend.position = '') +
        ylab('Far minus Near') +
        xlab('')

data_summary %>%
        filter(hidden_pa_img_type != 'all_pa') %>%
        droplevels() %>%
        
        pivot_wider(id_cols = c(ptp,
                                counterbalancing,
                                condition),
                    names_from = hidden_pa_img_type,
                    values_from = learning_rate_two_param) %>% 
        mutate(far_minus_near = far - near) %>%
        
        ggplot(aes(x=condition,
                   y=far_minus_near,
                   fill=condition)) +
        geom_violin(alpha = 0.2) +
        geom_boxplot(width=0.1,
                     fatten=4,
                     outlier.shape = '') +
        # geom_jitter(height = 0,
        #             width = 0.06,
        #             alpha = 0.3) +
        geom_line(aes(group=ptp),
                  alpha = 0.1) +
        geom_point(alpha = 0.2) +
        stat_summary(fun=mean,
                     color='red',
                     size=1) +
        ggtitle('LR 2 raw, comparing conditions, Far-Near') +
        geom_hline(yintercept = 0, linetype = 'dashed') +
        theme(legend.position = '') +
        ylab('Far minus Near') +
        xlab('')

data_summary %>%
        filter(hidden_pa_img_type != 'all_pa') %>%
        droplevels() %>%
        
        pivot_wider(id_cols = c(ptp,
                                counterbalancing,
                                condition),
                    names_from = hidden_pa_img_type,
                    values_from = learning_rate_two_param_G) %>% 
        mutate(far_minus_near = far - near) %>%
        
        ggplot(aes(x=condition,
                   y=far_minus_near,
                   fill=condition)) +
        geom_violin(alpha = 0.2) +
        geom_boxplot(width=0.1,
                     fatten=4,
                     outlier.shape = '') +
        # geom_jitter(height = 0,
        #             width = 0.06,
        #             alpha = 0.3) +
        geom_line(aes(group=ptp),
                  alpha = 0.1) +
        geom_point(alpha = 0.2) +
        stat_summary(fun=mean,
                     color='red',
                     size=1) +
        ggtitle('LR 2 raw gaussianized, comparing conditions, Far-Near') +
        geom_hline(yintercept = 0, linetype = 'dashed') +
        theme(legend.position = '') +
        ylab('Far minus Near') +
        xlab('')

```


# Parameter Bayes factors

## 2 Parameter model

### Schema 6-0 far vs near

```{r learning-rate-bayes-analysis-schema-c-far-vs-near}

data_for_bf_schema_6_0_far_vs_near_lr <- data_summary %>%
        filter(hidden_pa_img_type != 'all_pa',
               hidden_pa_img_type != 'near_far_combined') %>%
        filter(condition == 'schema_6_0') %>%
        droplevels() %>% 
        
        pivot_wider(id_cols = c(ptp,
                                counterbalancing,
                                condition),
                    names_from = hidden_pa_img_type,
                    values_from = learning_rate_two_param_G) %>% 
        mutate(far_minus_near = far - near) %>% 
        select(far_minus_near) %>% .[[1]]

data_for_bf_schema_6_0_far_vs_near_lrg <- data_summary %>%
        filter(hidden_pa_img_type != 'all_pa',
               hidden_pa_img_type != 'near_far_combined') %>%
        filter(condition == 'schema_6_0') %>%
        droplevels() %>%
        
        pivot_wider(id_cols = c(ptp,
                                counterbalancing,
                                condition),
                    names_from = hidden_pa_img_type,
                    values_from = learning_rate_two_param_G) %>% 
        mutate(far_minus_near = far - near) %>%
        select(far_minus_near) %>% .[[1]]


null_interval <- c(-Inf,0)

bf_schema_6_0_far_vs_near_learning_rate <- reportBF(ttestBF(
        data_for_bf_schema_6_0_far_vs_near_lr,
        nullInterval = null_interval
)[1],4)

bf_schema_6_0_far_vs_near_learning_rate_g <- reportBF(ttestBF(
        data_for_bf_schema_6_0_far_vs_near_lrg,
        nullInterval = null_interval
)[1],4)

```

## Schema 2_2 vs 4_2

```{r learning-rate-bayes-analysis-schema-2_2-vs-4_2}

data_for_bf_schema_2_2_vs_4_2_lr <- data_summary %>%
        filter(hidden_pa_img_type == 'near_far_combined') %>%
        droplevels() %>%
        
        pivot_wider(id_cols = c(ptp,
                                counterbalancing),
                    names_from = condition,
                    values_from = learning_rate_two_param) %>% 
        mutate(schema_2_2_vs_4_2 = schema_2_2 - schema_4_2) %>% 
        select(schema_2_2_vs_4_2) %>% .[[1]]

data_for_bf_schema_2_2_vs_4_2_lrg <- data_summary %>%
        filter(hidden_pa_img_type == 'near_far_combined') %>%
        droplevels() %>%
        
        pivot_wider(id_cols = c(ptp,
                                counterbalancing),
                    names_from = condition,
                    values_from = learning_rate_two_param_G) %>% 
        mutate(schema_2_2_vs_4_2 = schema_2_2 - schema_4_2) %>% 
        select(schema_2_2_vs_4_2) %>% .[[1]]


null_interval <- c(-Inf,Inf)

bf_schema_2_2_vs_4_2_learning_rate <- reportBF(ttestBF(
        data_for_bf_schema_2_2_vs_4_2_lr,
        nullInterval = null_interval
)[1],4)

bf_schema_2_2_vs_4_2_learning_rate_g <- reportBF(ttestBF(
        data_for_bf_schema_2_2_vs_4_2_lrg,
        nullInterval = null_interval
)[1],4)

```


## Schema 4_4 vs 4_2

```{r learning-rate-bayes-analysis-schema-4_4-vs-4_2}

data_for_bf_schema_4_4_vs_4_2_lr <- data_summary %>%
        filter(hidden_pa_img_type == 'near_far_combined') %>%
        droplevels() %>%
        
        pivot_wider(id_cols = c(ptp,
                                counterbalancing),
                    names_from = condition,
                    values_from = learning_rate_two_param) %>% 
        mutate(schema_4_4_vs_4_2 = schema_4_4 - schema_4_2) %>% 
        select(schema_4_4_vs_4_2) %>% .[[1]]

data_for_bf_schema_4_4_vs_4_2_lrg <- data_summary %>%
        filter(hidden_pa_img_type == 'near_far_combined') %>%
        droplevels() %>%
        
        pivot_wider(id_cols = c(ptp,
                                counterbalancing),
                    names_from = condition,
                    values_from = learning_rate_two_param_G) %>% 
        mutate(schema_4_4_vs_4_2 = schema_4_4 - schema_4_2) %>% 
        select(schema_4_4_vs_4_2) %>% .[[1]]

data_for_bf_schema_4_4_vs_4_2_lrg_no_outlier <- data_summary %>%
        filter(hidden_pa_img_type == 'near_far_combined') %>%
        droplevels() %>%
        
        pivot_wider(id_cols = c(ptp,
                                counterbalancing),
                    names_from = condition,
                    values_from = learning_rate_two_param_no_outlier_G) %>% 
        mutate(schema_4_4_vs_4_2 = schema_4_4 - schema_4_2) %>% 
        select(schema_4_4_vs_4_2) %>% .[[1]]


null_interval <- c(-Inf,0)

bf_schema_4_4_vs_4_2_learning_rate <- reportBF(ttestBF(
        data_for_bf_schema_4_4_vs_4_2_lr,
        nullInterval = null_interval
)[1],4)

bf_schema_4_4_vs_4_2_learning_rate_g <- reportBF(ttestBF(
        data_for_bf_schema_4_4_vs_4_2_lrg,
        nullInterval = null_interval
)[1],4)

bf_schema_4_4_vs_4_2_learning_rate_g_no_outlier <- reportBF(ttestBF(
        data_for_bf_schema_4_4_vs_4_2_lrg_no_outlier,
        nullInterval = null_interval
)[1],4)

```

# Effect size estimates

## 2 parameter model

### Schema 6-0 far vs near

### Schema_2_2 vs 4_2

### Schema 4_4 vs 4_2

```{r effect-size-4-4-vs-4-2}

data_summary %>%
        filter(hidden_pa_img_type == 'near_far_combined') %>%
        droplevels() %>%
        select(ptp,condition,learning_rate_two_param_no_outlier_G)

es_block_2_conditions <- idf %>%
        cohens_d(block_2_mouse_error_mean_LOG ~ condition, 
                 paired = TRUE, 
                 var.equal = FALSE,
                 # comparisons = list(c("schema_c","schema_ic"),),
                 hedges.correction = FALSE)

```


# Learning curve plots

## Plot outlier data

```{r learning-curves-outliers, fig.height=10, fig.width=15}

outlier_ptp <- data_summary %>%
        filter(outside_iqr_two_param == T,
               hidden_pa_img_type == 'near_far_combined') %>%
        droplevels() %>%
        select(ptp) %>% .[[1]] %>% as.character() %>% unique()

# Plot the fits
fig_each_ptp <- mean_by_rep_long_all_types %>%
        filter(hidden_pa_img_type == 'near_far_combined',
               border_dist_closest == 'all',
               ptp %in% outlier_ptp) %>%
        droplevels() %>%
        ggplot(aes(x=hidden_pa_img_row_number_across_blocks,
                   y=mouse_error_mean)) +
        geom_vline(xintercept = 4.5, linetype = 'dashed') +

        geom_point(alpha=0.5) +
        geom_line(alpha=0.5) +


        # Add the y_hat two parameters
        geom_line(aes(x=hidden_pa_img_row_number_across_blocks,
                      y=y_hat_two_param),
                  size=1,
                  color='red',
                  linetype = 'twodash') +

        # Add the y_hat three parameters
        geom_line(aes(x=hidden_pa_img_row_number_across_blocks,
                      y=y_hat_three_param),
                  size=1,
                  color='blue',
                  linetype = 'longdash') +

        geom_text(data=filter(
                data_summary,
                hidden_pa_img_type == 'near_far_combined',
                outside_iqr_two_param == T,
                ),
                aes(x=4.5,
                    y=250,
                    label = paste('int=',
                                  as.character(round(intercept_two_param,2)),
                                  ' ',
                                  'rate=',
                                  as.character(round(learning_rate_two_param,2)),
                                  seq='')),
                color = 'red') +
        geom_text(data=filter(
                data_summary,
                hidden_pa_img_type == 'near_far_combined',
                outside_iqr_two_param == T,
                ),
                aes(x=4.5,
                    y=200,
                    label = paste('int=',
                                  as.character(round(intercept_three_param,2)),
                                  ' ',
                                  'rate=',
                                  as.character(round(learning_rate_three_param,2)),
                                  seq='')),
                color = 'blue') +


        facet_grid(ptp~condition) +
        ggtitle(paste('Mouse euclidean distance',sep='')) +
        xlab('Image repetition') +
        ylab('Mouse euclidean distance ') +
        scale_x_continuous(breaks=c(1,2,3,4,5,6,7,8)) +
        scale_y_continuous(breaks=seq(0,250,50)) +
        theme(legend.position = '') +
        theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())

print(fig_each_ptp)


```



## All data, each condition

```{r raw-learning-curves-and-fits, fig.width=13, fig.height=100}


# Plot the fits
fig_each_ptp <- mean_by_rep_long_all_types %>%
        filter(hidden_pa_img_type == 'near_far_combined',
               border_dist_closest == 'all') %>%
        droplevels() %>%
        ggplot(aes(x=hidden_pa_img_row_number_across_blocks,
                   y=mouse_error_mean)) +
        geom_vline(xintercept = 4.5, linetype = 'dashed') +

        geom_point(alpha=0.5) +
        geom_line(alpha=0.5) +


        # Add the y_hat two parameters
        geom_line(aes(x=hidden_pa_img_row_number_across_blocks,
                      y=y_hat_two_param),
                  size=1,
                  color='red',
                  linetype = 'twodash') +

        # Add the y_hat three parameters
        geom_line(aes(x=hidden_pa_img_row_number_across_blocks,
                      y=y_hat_three_param),
                  size=1,
                  color='blue',
                  linetype = 'longdash') +

        geom_text(data=filter(
                data_summary,
                hidden_pa_img_type == 'near_far_combined',
                ),
                aes(x=4.5,
                    y=250,
                    label = paste('int=',
                                  as.character(round(intercept_two_param,2)),
                                  ' ',
                                  'rate=',
                                  as.character(round(learning_rate_two_param,2)),
                                  seq='')),
                color = 'red') +
        geom_text(data=filter(
                data_summary,
                hidden_pa_img_type == 'near_far_combined',
                ),
                aes(x=4.5,
                    y=200,
                    label = paste('int=',
                                  as.character(round(intercept_three_param,2)),
                                  ' ',
                                  'rate=',
                                  as.character(round(learning_rate_three_param,2)),
                                  seq='')),
                color = 'blue') +


        facet_grid(ptp~condition) +
        ggtitle(paste('Mouse euclidean distance',sep='')) +
        xlab('Image repetition') +
        ylab('Mouse euclidean distance ') +
        scale_x_continuous(breaks=c(1,2,3,4,5,6,7,8)) +
        scale_y_continuous(breaks=seq(0,250,50)) +
        theme(legend.position = '') +
        theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())

print(fig_each_ptp)

```

## All data, overlaid

```{r learning-curves-across-part, fig.width=7, fig.height=6}

# Plot the fits
fig_each_ptp <- mean_by_rep_long_all_types %>%
        filter(hidden_pa_img_type == 'near_far_combined',
               border_dist_closest == 'all') %>%
        droplevels() %>%                
        group_by(condition,
                 hidden_pa_img_row_number_across_blocks) %>%
        summarise(n = n(),
                  mouse_error_mean_across_ptp = mean(mouse_error_mean,na.rm = T),
                  mouse_error_sd_across_ptp = sd(mouse_error_mean, na.rm = T),
                  sem = mouse_error_sd_across_ptp/sqrt(n),
                  upper_95_ci = mouse_error_mean_across_ptp + qt(0.975,df = n-1)*sem,
                  lower_95_ci = mouse_error_mean_across_ptp - qt(0.975,df = n-1)*sem) %>% 
        ungroup() %>% 
        ggplot(aes(x=hidden_pa_img_row_number_across_blocks,
                   y=mouse_error_mean_across_ptp,
                   color=condition)) +
        geom_point(size=2) +
        geom_line(size=1) +
        # geom_ribbon(aes(ymin = lower_95_ci, 
        #                 ymax = upper_95_ci,
        #                 group=condition,
        #                 color=condition),
        #             alpha = 0.1) +

        # facet_grid(~condition) +
        ggtitle(paste('Mouse euclidean distance; Across participants',sep='')) +
        xlab('Image repetition') +
        ylab('Mouse euclidean distance ') +
        scale_x_continuous(breaks=c(1,2,3,4,5,6,7,8)) +
        scale_y_continuous(breaks=seq(0,200,25)) +  
        coord_cartesian(ylim = c(0,200)) +
        # theme(legend.position = 'top') +
        geom_vline(xintercept = 4.5, linetype = 'dashed') +
        theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())        



print(fig_each_ptp)


```

## Near vs far

```{r landmark-raw-learning-curves-and-fits, fig.width=18, fig.height=100}
if (plot_fits_near_far){
        # For mouse euclidean distance
        
        fig_each_ptp_lm <- mean_by_rep_long_all_types %>%
                filter(hidden_pa_img_type %in% c('near','far'),
                       !condition %in% c('random_locations','no_schema'),
                       border_dist_closest == 'all'
                       ) %>%
                droplevels() %>%
                
                ggplot(aes(x=hidden_pa_img_row_number_across_blocks,
                           y=mouse_error_mean,
                           group=hidden_pa_img_type,
                           color=hidden_pa_img_type)) +
                geom_point(size=2) +
                geom_line(size=0.5) +
        
                # Add the y_hat learning and intercept
                geom_line(aes(x=hidden_pa_img_row_number_across_blocks,
                              y=y_hat_two_param),
                          size=0.8,
                          # color='blue',
                          linetype = 'twodash') +
                
                # Add the y_hat learning and intercept
                geom_line(aes(x=hidden_pa_img_row_number_across_blocks,
                              y=y_hat_three_param),
                          size=0.8,
                          # color='blue',
                          linetype = 'longdash') +
                
                
                facet_grid(ptp~condition) +
                ggtitle('Mouse euclidean distance') +
                xlab('Image repetition') +
                ylab('Mouse euclidean distance') +
                scale_x_continuous(breaks=c(1,2,3,4,5,6,7,8)) +
                scale_y_continuous(breaks=seq(0,250,50)) +
        
                # theme(legend.position = 'top') +
                geom_vline(xintercept = 4.5, linetype = 'dashed') +
                # theme(legend.position = '') +
                theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())        
        
        
        print(fig_each_ptp_lm)
}

```

## Near vs far, across-participants

```{r landmark-raw-learning-curves-and-fits-overlaid, fig.width=8, fig.height=5}

# For mouse euclidean distance

fig_each_ptp_lm <- mean_by_rep_long_all_types %>%
        filter(hidden_pa_img_type %in% c('near','far'),
               !condition %in% c('random_locations','no_schema'),
               border_dist_closest == 'all'
               ) %>%
        droplevels() %>%
        
        group_by(condition,
                 hidden_pa_img_type,
                 hidden_pa_img_row_number_across_blocks) %>%
        summarise(n = n(),
                  mouse_error_mean_across_ptp = mean(mouse_error_mean,na.rm = T)) %>% 
        ungroup() %>%
        ggplot(aes(x=hidden_pa_img_row_number_across_blocks,
                   y=mouse_error_mean_across_ptp,
                   color=condition,
                   linetype=hidden_pa_img_type)) +        
        
        geom_point(size=1) +
        geom_line(size=0.5) +

        ggtitle('Mouse euclidean distance') +
        xlab('Image repetition') +
        ylab('Mouse euclidean distance') +
        scale_x_continuous(breaks=c(1,2,3,4,5,6,7,8)) +
        scale_y_continuous(breaks=seq(0,250,50)) +

        # theme(legend.position = 'top') +
        geom_vline(xintercept = 4.5, linetype = 'dashed') +
        # theme(legend.position = '') +
        theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())        


print(fig_each_ptp_lm)


```


## Near vs far difference across trials:

```{r near-far-diff-across-reps, fig.width=20, fig.height=20}

fig <- mean_by_rep_long_all_types %>%
        filter(hidden_pa_img_type %in% c('near','far'),
               !condition %in% c('random_locations','no_schema'),
               border_dist_closest == 'all'
               ) %>%
        droplevels() %>%

        pivot_wider(id_cols = c(ptp,
                                counterbalancing,
                                condition,
                                hidden_pa_img_row_number_across_blocks),
                    names_from = hidden_pa_img_type,
                    values_from = mouse_error_mean) %>% 
        mutate(far_minus_near = far - near) %>% 
        
        
        ggplot(aes(x=hidden_pa_img_row_number_across_blocks,
                   y=far_minus_near,
                   color=condition,
                   group=condition)) +        
        
        geom_point(size=1) +
        geom_line(size=0.5) +

        facet_wrap(~ptp) +
        ggtitle('Mouse euclidean distance') +
        xlab('Image repetition') +
        ylab('Mouse euclidean distance') +
        scale_x_continuous(breaks=c(1,2,3,4,5,6,7,8)) +
        scale_y_continuous(breaks=seq(0,250,50)) +

        # theme(legend.position = 'top') +
        geom_vline(xintercept = 4.5, linetype = 'dashed') +
        geom_hline(yintercept = 0, linetype = 'dashed') +
        # theme(legend.position = '') +
        theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())        


print(fig)


```

## Near vs far diff, across participants:

```{r near-far-diff-across-reps-overlaid, fig.width=7, fig.height=5}

fig <- mean_by_rep_long_all_types %>%
        filter(hidden_pa_img_type %in% c('near','far'),
               !condition %in% c('random_locations','no_schema'),
               border_dist_closest == 'all'
               ) %>%
        droplevels() %>%

        pivot_wider(id_cols = c(ptp,
                                counterbalancing,
                                condition,
                                hidden_pa_img_row_number_across_blocks),
                    names_from = hidden_pa_img_type,
                    values_from = mouse_error_mean) %>% 
        mutate(far_minus_near = far - near) %>% 
        
        group_by(condition,
                 hidden_pa_img_row_number_across_blocks) %>%
        summarise(n = n(),
                  far_minus_near_mean_across_ptp = mean(far_minus_near,na.rm = T)) %>% 
        ungroup() %>%

        ggplot(aes(x=hidden_pa_img_row_number_across_blocks,
                   y=far_minus_near_mean_across_ptp,
                   color=condition,
                   group=condition)) +        
        
        geom_point(size=1) +
        geom_line(size=0.5) +

        ggtitle('Far minus Near') +
        xlab('Image repetition') +
        ylab('Far minus Near') +
        scale_x_continuous(breaks=c(1,2,3,4,5,6,7,8)) +
        scale_y_continuous(breaks=seq(-100,100,10)) +

        # theme(legend.position = 'top') +
        geom_vline(xintercept = 4.5, linetype = 'dashed') +
        geom_hline(yintercept = 0, linetype = 'dashed') +
        # theme(legend.position = '') +
        theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())        


print(fig)


```
